Improving INTEGRAL/SPI data analysis of GRBs

### 2022-03-01 src/ms.tex
add \

BB{\citet{Bosnjak-2014} did a joined analysis of SPI and the Imager on Board the INTEGRAL Satellite (IBIS) data of GRBs to create a spectral catalque of INTEGRAL GRBs \citep{Ubertini-2003}. They construct a response for every SPI detector and forward model the photon model directly into the data space of every detector, which is similar to our approach in this work. But following their paper we see three main differences compared to our methods: Background treatment, response generation and PSD events.\\
In the paper the authors argue that background subtracting is better than using a model template for the background within OSA, as well as cite Cash 1979 \citep{Cash-1979} for their likelihood. Therefore we conclude that they used a Poisson likelihood on the background subtracted data. This is different to our approach and it has been shown that using background subtraction can give misleading results \citep[e.g.][]{Greiner-2016}. For the response generation the authors in \citet{Bosnjak-2014} state that they calculate a response function taking into account the exposed fraction of each detector for the GRB position and that for a detector completely shadowed the net spectrum is zero. Therefore we conclude that they used an idealistic mask with zero transparency at all energies. We on the other hand used the official response simulations that also include some transparency, especially at high energies. The last point are the PSD events, which are ignored completely in \citet{Bosnjak-2014}. \citet{spi_electronic_noise} have shown that the effect of the PSD events gets stronger for bright sources, therefore it is important to account for this effect in the case of GRBs.\\
Unfortunately the software used in \citet{Bosnjak-2014} is not public, so we can not compare our method with theirs directly.}

>>>>

\BB{\citet{Bosnjak-2014} did a joined analysis of SPI and the Imager on Board the INTEGRAL Satellite (IBIS) data of GRBs to create a spectral catalque of INTEGRAL GRBs \citep{Ubertini-2003}. They construct a response for every SPI detector and forward model the photon model directly into the data space of every detector, which is similar to our approach in this work. But following their paper we see three main differences compared to our methods: Background treatment, response generation and PSD events.\\
In the paper the authors argue that background subtracting is better than using a model template for the background within OSA, as well as cite Cash 1979 \citep{Cash-1979} for their likelihood. Therefore we conclude that they used a Poisson likelihood on the background subtracted data. This is different to our approach and it has been shown that using background subtraction can give misleading results \citep[e.g.][]{Greiner-2016}. For the response generation the authors in \citet{Bosnjak-2014} state that they calculate a response function taking into account the exposed fraction of each detector for the GRB position and that for a detector completely shadowed the net spectrum is zero. Therefore we conclude that they used an idealistic mask with zero transparency at all energies. We on the other hand used the official response simulations that also include some transparency, especially at high energies. The last point are the PSD events, which are ignored completely in \citet{Bosnjak-2014}. \citet{spi_electronic_noise} have shown that the effect of the PSD events gets stronger for bright sources, therefore it is important to account for this effect in the case of GRBs.\\
Unfortunately the software used in \citet{Bosnjak-2014} is not public, so we can not compare our method with theirs directly.}
